### 2016-07-27 Chapters/Ch04-PaperSummary.tex
Add commands, fix notations

%************************************************
\chapter{Summary of the papers}\label{ch:papers-summary}

@@

\section{Paper I. Continuum solvation in the relativistic regime}

@@

\section{Paper II. The wavelet boundary element method for PCM}
\section{Paper III: Continuum modelling of non homogeneous environments}

>>>>

% mainfile: ../RobertoDiRemigioPhDThesis.tex
%************************************************
\chapter{Summary of the papers}\label{ch:papers-summary}

In the following, I provide a brief summary of the motivations, contents and
conclusions of the papers this thesis is based on.
In addition, I give a description of my contributions to the work leading to
the publication of each of the papers.
\todo[inline]{Write something along these lines: "My coauthors have all read and approved."}

\section*{Software}

@@

\section*{Paper I. Continuum solvation in the relativistic regime}

Systems containing heavy elements are notoriously challenging for quantum chemistry.
In addition to their significantly large sizes, one has to properly include the
effect of special relativity in the quantum chemical description in order to
achieve at least qualitative agreement with experiment.
Additional complications arise if one needs to also include environment effects.
Continuum models arguably represent a cost-effective strategy to achieve a first
approximation of these effects.
In this paper, we presented the first derivation and implementation of the \acs{PCM}
coupled to a \acs{SCF} description of the solute in the fully relativistic, four-component
regime.

@@

\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

Continuum solvation models are inherently parametrized. Apart from solvent permittivities,
the atomic radii and molecular surface definition play a crucial role
in determining the performance of the models.
However, the numerical accuracy of the \acs{BEM} procedure used to numerically solve the
underlying \acs{BIE} is a not-so-often studied aspect of these models.
Traditionally, collocation methods have been used, but these require parametrization of some of the necessary surface integrals.
Galerkin methods do not suffer from such a limitation and additionally preserve symmetry of the underlying
boundary integral operators.
The use of biorthogonal wavelet bases as finite elements achieves sparsity in
the \acs{BEM} procedure, due to their intrinsically hierarchical structure and
the existence of \emph{a priori} and \emph{a posteriori} matrix compression
estimates.
Thus, wavelet Galerkin \acs{BEM} represents a valid alternative to traditional collocation methods,
both to achieve a better computational scaling and to provide accurate, benchmark results.

This work builds upon and extends previous work by~\citeauthor{Weijo2010-hy}
\citeauthor{Weijo2010-hy} used \ac{PWC} bases to show that superior accuracy
and convergence could be obtained for the calculation of molecular energies.
In this work we showed that faster convergence can be achieved when \ac{PWL} bases are used instead.
Moreover, the same holds for the calculation of static electric properties.
Notably, the traditional collocation solver cannot guarantee the same accuracy,
even for very large finite element bases. This suggests that, in some cases,
\acs{BEM} collocation methodologies might slow down or even prevent the
convergence of the quantum mechanical response equations solvers.

For this paper, I provided template interface and test sets for the cavity
generator\autocite{Harbrecht2009-no, Harbrecht2011-dk}
and wavelet Galerkin \acs{BEM} solver\autocite{Harbrecht2004-uo, Harbrecht2006-ug, Dahmen2006-pj}
with \pcmsolver.
These were used to interface with the new C++ implementation of the wavelet
Galerkin solvers of Monica Bugeanu.
I implemented the interface between the \LSDALTON quantum chemistry software
package and the \pcmsolver software library. The interface allows to run \acs{HF} and
\acs{KS}-\acs{DFT} single-point and linear response calculations.
I, together with coauthor Krzysztof Mozgawa, performed the benchmark quantum
chemical calculations presented in the paper.
Finally, I coordinated the editing of all manuscript drafts. I wrote Sections 2.1 and 2.3,
while Sections 3 and 4 were co-written with the first author, Monica Bugeanu.
I performed most of the data analysis and produced tables and graphs.

The interface to \LSDALTON was later released in version ...
providing \acs{PCM} capabilities to the software package.

\section*{Paper III: Continuum modelling of non homogeneous environments}

### 2016-07-27 FrontBackmatter/Notation.tex
Add commands, fix notations

%A number of notations and typographic conventions has been adopted in order to maintain consistency throughout. We summarize them here:
%\begin{table*}[!h]
%\begin{tabular}{c l}
% $\mathcal{A}, \mathcal{D}, \ldots$ & integral operators over a closed subset of $\mathbb{R}^2$ \\
% $H, \varPhi, \ldots$ & first or second quantized $N$-electron operators \\
% $\vect{r}, \vect{r}^\prime, \ldots$ & position vectors in $\mathbb{R}^3$ \\
% $\vect{s}, \vect{s}^\prime, \ldots$ & position vectors in a closed subset of $\mathbb{R}^2$ \\
% $\vect{v}, \vect{q}, \ldots$ & vectors in an arbitrary vector space \\
% $\mat{K}, \mat{F}, \ldots$ & matrices in an arbitrary vector space \\
% $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
%\end{tabular}
%\end{table*}
%
%Summation over repeated indices, both discrete and continuous, is always to be understood:
%\begin{alignat*}{2}
% f_r = C_{\kappa r}g_{\kappa} \equiv \sum_{\kappa}C_{\kappa r}g_{\kappa}, \quad&\quad
% f(\vect{r}) = U(\vect{r},\vect{r}^\prime)g(\vect{r}^\prime) \equiv \int\diff\vect{r}^\prime U(\vect{r},\vect{r}^\prime)g(\vect{r}^\prime).
%\end{alignat*}
%
%Further conventions have been adopted for the indices of functions. Lower case Latin letters are used for MO 4-spinors, while lower case
%Greek letters ($\kappa, \lambda, \mu, \ldots$) are reserved for one-electron basis functions in 2-spinor or scalar form.
%Specific ranges of letters are used as follows:
%\begin{table*}[!h]
%\begin{tabular}{c l}
% $r, s, t, \ldots$ & general MO 4-spinor indices \\
% $i, j, k, \ldots$ & occupied MO 4-spinor indices \\
% $a, b, c, \ldots$ & virtual MO 4-spinor indices
%\end{tabular}
%\end{table*}
%
%Upper case Latin letters always refer to functions in vector spaces other than the two listed above. Complex conjugation will always be shown using
%a dagger ($\dagger$) instead of a star ($*$).
%
%SI-based atomic units have been used \cite{Whiffen1978}:
%\begin{equation*}
% \si{\electronmass} = \si{\elementarycharge} = \hslash = \frac{1}{4\pi\diel_0} = 1
%\end{equation*}
%the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
%The speed of light is then:
%\begin{equation*}
% c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
%\end{equation*}
%
%
%Some useful conversion constants to SI units are here listed \cite{CODATA2010}:
%\begin{subequations}
% \begin{align*}
%  \SI{1}{\bohr} &= \SI{0.52917721092}{\angstrom} = \SI{5.2917721092e-11}{\meter} \\
%  \SI{1}{\hartree} &= \SI{27.21138505}{\electronvolt} = \SI{2625.4996404}{\kilo\joule\per\mole} \\
%  \SI{1}{\debye} &= \SI{3.3356410E-30}{\coulomb\meter} \\
%  \SI{1}{\angstrom\cubed} &= \SI{1.11264984E-40}{\coulomb\squared\meter\squared\per\joule}
% \end{align*}
%\end{subequations}

>>>>

A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here:
\begin{table*}[!h]
\begin{tabular}{c l}
 $\bi{A}, \bi{D}, \ldots$ & integral operators over a closed subset of $\mathbb{R}^2$ \\
 $H, \varPhi, \ldots$ & first or second quantized $N$-electron operators \\
 $\vect{r}, \vect{r}^\prime, \ldots$ & position vectors in $\mathbb{R}^3$ \\
 $\vect{s}, \vect{s}^\prime, \ldots$ & position vectors in a closed subset of $\mathbb{R}^2$ \\
 $\vect{v}, \vect{q}, \ldots$ & vectors in an arbitrary vector space \\
 $\mat{K}, \mat{F}, \ldots$ & matrices in an arbitrary vector space \\
 $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
\end{tabular}
\end{table*}

Further conventions have been adopted for the indices of functions.
Lower case Latin letters are used for MO 4-spinors, while lower case
Greek letters ($\kappa, \lambda, \mu, \ldots$) are reserved for
one-electron basis functions in 2-spinor or scalar form.
Specific ranges of letters are used as follows:
\begin{table*}[!h]
\begin{tabular}{c l}
 $r, s, t, \ldots$ & general MO 4-spinor indices \\
 $i, j, k, \ldots$ & occupied MO 4-spinor indices \\
 $a, b, c, \ldots$ & virtual MO 4-spinor indices
\end{tabular}
\end{table*}

Upper case Latin letters always refer to functions in vector spaces
other than the two listed above. Complex conjugation will always be
shown using a dagger ($\dagger$) instead of a star ($*$).

Hartree atomic units have been used:~\autocite{Whiffen1978}
\begin{equation*}
 \si{\electronmass} = \si{\elementarycharge} = \hslash = 4\pi\diel_0 = 1
\end{equation*}
the unit of length is the Bohr \si{\bohr}, while that of energy is the Hartree \si{\hartree}.
The speed of light is then:
\begin{equation*}
 c = \SI{137.035999074}{\bohr\hartree\per\planckbar}
\end{equation*}

Some useful conversion constants to SI units are here
listed:~\autocite{Mohr2012-zc}
\begin{subequations}
 \begin{align*}
  \SI{1}{\bohr} &= \SI{0.52917721092}{\angstrom} = \SI{5.2917721092e-11}{\meter} \\
  \SI{1}{\hartree} &= \SI{27.21138505}{\electronvolt} = \SI{2625.4996404}{\kilo\joule\per\mole} \\
  \SI{1}{\debye} &= \SI{3.3356410E-30}{\coulomb\meter} \\
  \SI{1}{\angstrom\cubed} &= \SI{1.11264984E-40}{\coulomb\squared\meter\squared\per\joule}
 \end{align*}
\end{subequations}
